Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-06-27 manuscript/coverletter_resub.tex
possibly ready to send out to coauthors

		[[Not sure this is the best angle.]]
		Plants' interactions with animals can significantly affect their fitness, both positively and negatively. These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be if there is selection to avoid overlap with close relatives or if distant relatives converge. By comparing plant families displaying different patterns of conservation of these interactions, we can predict which families may experience different types of selection pressures. Thus, we can use ecological data to guide future evolutionary research.

@@

	Note that we submitted an earlier version of this manuscript to New Phytologist, for which the revision period expired in August 2017. We now use a different methodology from that presented in the initial submission, and we are happy to have the current version stand on its own merits as a new initial submission. We hope that you will agree that the question we investigate remains of interest to the readership of \textbf{New Phytologist}.

>>>>

		Plants' interactions with animals can significantly affect their fitness, both positively and negatively. These interactions might be conserved through stabilising selection or if key traits affecting the interactions are highly heritable, or they might not be if there is selection to avoid overlap with close relatives or if distant relatives converge. The question of whether, and how strongly, plants' interaction partners are phylogenetically conserved has excited continuing interest, as it is likely an important step towards understanding the eco-evolutionary dynamics of plant-insect communities. Within this context, our work takes one step beyond considering whole-network trends to examine variation between plant families. We believe that this finer-grained approach will be critical in future efforts to find the mechanisms driving conservationof interaction partners.

		We note that our manuscript shares some methodological similarities with another important and timely article: Fontaine \& Th\'{e}bault, 2015 (Population Ecology). Due to the long gestation of this manuscript, we believe that the two manuscripts were developed independently. Nevertheless, we respect their prior publication and have taken care to refer to it in our manuscript. Our manuscript does, however, include a few methodological innovations which greatly add to its novelty. First, we define overlap in interaction partners using numbers of shared and not-shared partners (analogous to numbers of successes and failures in Bernoulli trials). This approach, as opposed to using only the number or propotion of shared interaction partners, effectively weights our data according to how much information is available and appears to be a more powerful tool to detect weak trends. Second, in addition to overall trends at the network level, we also test whether these trends are related to community composition and whether different plant families show different trends. These more-detailed analyses complement the usual network-level approach to give more insight into potential drivers of conservation of interaction partners. We believe that these additions to our methodology are enough to distinguish our work from that of Fontaine \& Th\'{e}bault. ]]

@@

	Note that we submitted an earlier version of this manuscript to New Phytologist, for which the revision period expired in August 2017. As the lead author was completing her PhD and transitioning to a postdoctoral appointment in a different country, we hope that the Editorial team will understand our failure to meet the original deadline. While we have taken the comments provided on the earlier version to heart, we now use a very different methodology and have revised the entire manuscript. We are therefore happy to have the current version stand on its own merits as a new initial submission, but are also prepared to provide a response to the previous round of comments if requested. Despite the delay, we hope that you will agree that the question we investigate remains of interest to the readership of \textbf{New Phytologist}.
